---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# YuweiLuoAssignmentB2

<!-- badges: start -->
<!-- badges: end -->

The goal of YuweiLuoAssignmentB2 is to calculate the Tibble or data frame column summary information(max, min, mean, median, standard deviation).

## Installation

You can install the development version from [GitHub](https://github.com/) with:

``` {r}
#devtools::install_github("stat545ubc-2021/YuweiLuoAssignmentB2")
```
## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(YuweiLuoAssignmentB2)

#max info calculation example
summaryInfoCal(palmerpenguins::penguins, "max", "body_mass_g", "sex")

#min info calculation example
summaryInfoCal(palmerpenguins::penguins, "min", "body_mass_g", "sex")

#mean info calculation example
summaryInfoCal(palmerpenguins::penguins, "mean", "body_mass_g", "sex")

#median info calculation example
summaryInfoCal(palmerpenguins::penguins, "median", "body_mass_g", "sex")

#sd info calculation example
summaryInfoCal(palmerpenguins::penguins, "sd", "body_mass_g", "sex")


```

For more information, please refer to the development documentation of function by running ```?summaryInfoCal``` in the **Console** of **RStudio**.
