---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# YuweiLuoAssignmentB2 Info

<!-- badges: start -->
<!-- badges: end -->

The goal of YuweiLuoAssignmentB2 package is to calculate the Tibble or data frame column summary information(max, min, mean, median, standard deviation).

## Description of package

package **YuweiLuoAssignmentB2** contains a function named `summaryInfoCal()`.

function **summaryInfoCal()** returns tibble or data frame summary information for col_name input based on category input.


## Installation

**YuweiLuoAssignmentB2** is not yet on CRAN. But, You can install the development version from [GitHub](https://github.com/) with:

``` {r}
#devtools::install_github("stat545ubc-2021/YuweiLuoAssignmentB2")
```
## Example

These are 4 basic examples which shows you how to use **summaryInfoCal()** function. 


```{r example}
library(YuweiLuoAssignmentB2)

#max info calculation example
summaryInfoCal(palmerpenguins::penguins, "max", "body_mass_g", "sex")

#min info calculation example
summaryInfoCal(palmerpenguins::penguins, "min", "body_mass_g", "sex")

#mean info calculation example
summaryInfoCal(palmerpenguins::penguins, "mean", "body_mass_g", "sex")

#median info calculation example
summaryInfoCal(palmerpenguins::penguins, "median", "body_mass_g", "sex")

#sd info calculation example
summaryInfoCal(palmerpenguins::penguins, "sd", "body_mass_g", "sex")


```

For more information, please refer to the development documentation of function by running ```?summaryInfoCal``` in the **Console** of **RStudio**.
